Dynamical modeling of tidal streams

### 2013-12-30 tex/ms.tex
streams: finish PDF section

@@

\acknowledgements It is a pleasure to thank \dots for helpful comments
and assistance. J.B. was supported by NASA through Hubble Fellowship
grant HST-HF-51285.01 from the Space Telescope Science Institute,
which is operated by the Association of Universities for Research in
Astronomy, Incorporated, under NASA contract NAS5-26555. J.B.
acknowledges support from SFB 881 (A3) funded by the German Research
Foundation DFG.

>>>>

\figurename~\ref{fig:gd1_pdf_xz} shows such PDFs of $p(Z|X)$ for a few
$X$ on the leading arm of the stream as well as the estimated Gaussian
PDFs determined using the procedure in
\sectionname~\ref{sec:trackxv}. It is clear that the average stream
location as calculated in \sectionname~\ref{sec:trackxv} is very close
to the actual average location of the stream in $(\vecx,\vecv)$ and
that the estimated dispersion is close to the true model
dispersion. The fact that the estimated Gaussian in the right panel is
only at the highest peak is by choice; there is an estimated Gaussian
dispersion at the lower peak as well.

Similar procedures can be followed to evaluate other projections and
marginalizations of the PDF, \eg, $p(b|l)$ for the observed track of
the stream on the sky, to convolve the PDF with observational
uncertainties, and to calculate moments of the PDF, \eg, the density
and velocity dispersion along the stream.

@@

\acknowledgements It is a pleasure to thank David W. Hogg, Hans-Walter
Rix, and Jason Sanders for helpful discussions. J.B. was supported by
NASA through Hubble Fellowship grant HST-HF-51285.01 from the Space
Telescope Science Institute, which is operated by the Association of
Universities for Research in Astronomy, Incorporated, under NASA
contract NAS5-26555. J.B.  acknowledges support from SFB 881 (A3)
funded by the German Research Foundation DFG.
